\documentclass[10pt]{article}
\usepackage[letterpaper,margin=0.8in]{geometry}
\usepackage{array,booktabs,longtable,tabularx,adjustbox,graphicx,textcomp,xcolor}
\usepackage{parskip}
\usepackage{hyperref}
\newcommand{\yes}{\textcolor{green!55!black}{\textbf{Yes}}}
\newcommand{\no}{\textcolor{red!70!black}{No}}
\newcommand{\na}{\textit{N/A}}
\newcommand{\conf}{\textcolor{orange!80!black}{Confirm}}
\title{\textbf{Supplementary Materials}\\[3pt]\large BCHAIN-ACCESS: An Accessibility-by-Design Framework Integrating Blockchain and HCI for Healthcare Interfaces}
\date{}
\begin{document}\maketitle
\noindent This supplement provides implementation-depth and audit material referenced from the main
paper. S1--S3 are development/feasibility artifacts recorded on a local Hardhat EVM node and are not
representative of production-network behaviour. S4--S6 support the security, accessibility-conformance,
and positioning claims. Cells marked \conf{} indicate values the authors should finalise against their
own audit logs and the public deposit (project repository: \url{https://github.com/mallisami/Bchain_Access-}, archived at Zenodo DOI \href{https://doi.org/10.5281/zenodo.21345578}{10.5281/zenodo.21345578}).

\section*{S1. Development-Network Gas Benchmarks}
Recorded on a local Hardhat EVM node (Solidity~0.8.19, optimizer enabled, 200 runs; 30{,}000{,}000~gas block limit; no congestion). Values are average \texttt{gasUsed} from the full reference implementation, in which the append-only audit log is written on-chain for HIPAA-style traceability; costs are correspondingly higher than a hash-only design would incur and are \emph{not} representative of mainnet, public-testnet, or Layer-2 costs. ETH estimates are illustrative at 20~Gwei.
\begin{center}\small\begin{tabular}{|l|r|r|l|}
\hline\textbf{Contract Function} & \textbf{EVM Gas} & \textbf{Est.\ ETH} & \textbf{Category}\\\hline
\texttt{registerRecord} & 341{,}873 & $\approx$0.0068 & Write (storage init + audit)\\\hline
\texttt{initiateGrant} & 386{,}111 & $\approx$0.0077 & Write (struct setup + audit)\\\hline
\texttt{confirmGrant} & 199{,}832 & $\approx$0.0040 & Modify (storage update + audit)\\\hline
\texttt{cancelPendingGrant} & 213{,}328 & $\approx$0.0043 & Modify (pending cleared + audit)\\\hline
\texttt{revokeAccess} & 171{,}927 & $\approx$0.0034 & Modify (de-activation + audit)\\\hline
\texttt{checkAccess} & 0 & 0 (free) & Read (\texttt{view})\\\hline
\texttt{getAuditLog} & 0 & 0 (free) & Read (\texttt{view})\\\hline
\textit{(deployment)} & 2{,}925{,}863 & $\approx$0.0585 & Deploy (9.8\% of block limit)\\\hline
\end{tabular}\end{center}
{\footnotesize Figures are average \texttt{gasUsed} over the evaluation workload and reflect the full Solidity implementation, including the on-chain append-only audit-log writes that accompany every state-changing call; \texttt{initiateGrant} varied across calls (380{,}412--400{,}360, avg.\ 386{,}111). Only 32-byte record hashes are stored on-chain; sensitive records remain off-chain.}

\section*{S2. Threat-Vector-to-Mitigation Matrix}
\begin{center}\small\begin{tabular}{|l|l|}
\hline\textbf{Threat vector} & \textbf{Implemented mitigation}\\\hline
Unauthorized access & \texttt{accessGrants} check + off-chain-encrypted records\\\hline
Replay attacks & EVM account nonces\\\hline
Coerced / accidental grants & 60\,s cooldown + \texttt{cancelPendingGrant()}\\\hline
Audit-log tampering & Append-only \texttt{AuditEntry[]}\\\hline
Sybil attacks & DAC whitelist model\\\hline
Front-running of a pending grant & \texttt{onlyPatient(msg.sender)} guard on \texttt{confirmGrant}\\\hline
\end{tabular}\end{center}

\section*{S3. Feature-by-Feature Architecture Comparison}
\begin{center}\small\begin{tabular}{|l|c|c|c|}
\hline\textbf{Property} & \textbf{Centralized EHR} & \textbf{Pure-Ethereum} & \textbf{BCHAIN-ACCESS}\\\hline
Patient data sovereignty & \no & Partial & \yes\\\hline
PII protection & DB-leak exposure & On-chain string exposure & On-chain hash only\\\hline
Two-phase time-locked window & \no & \no & \yes\\\hline
Immutable audit trail & \no & \yes & \yes\\\hline
Explicit WCAG-2.1-AA UI layer & \no & \no & \yes\\\hline
Access-check latency & --- & --- & $<$10\,ms (\texttt{view}, informal)\\\hline
\end{tabular}\end{center}

\section*{S4. Security Threat Model (STRIDE)}
STRIDE decomposition of \texttt{HealthAccessControl.sol}. ``Residual/next step'' items are scoped to the
independent audit (Limitation~L8) and public-testnet evaluation (L7).
\begin{center}\small
\begin{tabular}{|p{2.3cm}|p{5.4cm}|p{5.4cm}|}
\hline
\textbf{STRIDE category} & \textbf{Contract-level exposure} & \textbf{Mitigation / residual}\\\hline
\textbf{S}poofing (identity) & Impersonating a patient or provider address & EVM account keys + \texttt{onlyPatient(msg.sender)} binding; residual: key-management/HSM out of scope\\\hline
\textbf{T}ampering (data) & Altering records or grants & On-chain hash anchoring; append-only structures; off-chain records encrypted at rest (\conf{} KMS)\\\hline
\textbf{R}epudiation & Denying a grant/revoke occurred & Append-only \texttt{AuditEntry[]} audit log with immutable event trail\\\hline
\textbf{I}nformation disclosure & Leaking PII via chain data & Only 32-byte hashes on-chain; personal data off-chain; salted digests\\\hline
\textbf{D}enial of service & Blocking access or exhausting gas & \texttt{view} reads are free; bounded loops; residual: public-network gas/DoS under load unmeasured (L7)\\\hline
\textbf{E}levation of privilege & Gaining access without patient consent & Single-role \texttt{onlyPatient} modifier; two-phase time-locked confirmation; residual: static analysis (Slither/Mythril) recommended (see S6)\\\hline
\end{tabular}
\end{center}

\section*{S5. WCAG 2.1 Level AA Conformance Coverage Matrix}
Per-criterion coverage of the UI-layer prototype (Levels A + AA = 50 success criteria for AA conformance).
Status: \yes{} = implemented with the stated mechanism; \na{} = not applicable (no such content type);
\conf{} = present in the automated/code-review audit, authors to finalise against logs.
{\footnotesize (Media criteria 1.2.x are \na: the prototype contains no audio or video.)}
\begin{center}\footnotesize
\begin{longtable}{|l|p{5.3cm}|c|p{4.2cm}|}
\hline\textbf{SC} & \textbf{Success Criterion (Level)} & \textbf{Status} & \textbf{Mechanism / note}\\\hline\endhead
1.1.1 & Non-text Content (A) & \yes & Alt text on all images/icons\\\hline
1.2.1--1.2.5 & Time-based media (A/AA) & \na & No audio/video content\\\hline
1.3.1 & Info \& Relationships (A) & \yes & Semantic HTML + ARIA landmarks\\\hline
1.3.2 & Meaningful Sequence (A) & \yes & Logical DOM/reading order\\\hline
1.3.3 & Sensory Characteristics (A) & \yes & Instructions not colour/shape-only\\\hline
1.3.4 & Orientation (AA) & \conf & Responsive layout\\\hline
1.3.5 & Identify Input Purpose (AA) & \conf & Autocomplete tokens on inputs\\\hline
1.4.1 & Use of Colour (A) & \yes & Colour not sole indicator\\\hline
1.4.2 & Audio Control (A) & \na & No auto audio\\\hline
1.4.3 & Contrast (Minimum) (AA) & \yes & 29/29 pairs $\geq$4.5:1 (3:1 large)\\\hline
1.4.4 & Resize Text (AA) & \conf & Zoom to 200\% without loss\\\hline
1.4.5 & Images of Text (AA) & \yes & Real text, not images of text\\\hline
1.4.10 & Reflow (AA) & \conf & Reflow at 320\,CSS px\\\hline
1.4.11 & Non-text Contrast (AA) & \yes & UI components/focus $\geq$3:1\\\hline
1.4.12 & Text Spacing (AA) & \conf & No clipping under spacing override\\\hline
1.4.13 & Content on Hover/Focus (AA) & \conf & Dismissible/persistent tooltips\\\hline
2.1.1 & Keyboard (A) & \yes & Full keyboard operability\\\hline
2.1.2 & No Keyboard Trap (A) & \yes & Verified no trap\\\hline
2.1.4 & Character Key Shortcuts (A) & \na & No single-key shortcuts\\\hline
2.2.1 & Timing Adjustable (A) & \conf & 60\,s cooldown --- \textbf{make user-configurable} (open item; see main paper)\\\hline
2.2.2 & Pause, Stop, Hide (A) & \na & No moving/auto-updating content\\\hline
2.3.1 & Three Flashes (A) & \yes & No flashing; reduced-motion honoured\\\hline
2.4.1 & Bypass Blocks (A) & \yes & ``Skip to main content'' link\\\hline
2.4.2 & Page Titled (A) & \yes & Descriptive title\\\hline
2.4.3 & Focus Order (A) & \yes & Logical focus order\\\hline
2.4.4 & Link Purpose (In Context) (A) & \yes & Descriptive link text\\\hline
2.4.5 & Multiple Ways (AA) & \conf & Nav + direct actions\\\hline
2.4.6 & Headings \& Labels (AA) & \yes & Descriptive headings/labels\\\hline
2.4.7 & Focus Visible (AA) & \yes & Visible focus indicators\\\hline
2.5.1--2.5.4 & Pointer/Motion (A) & \conf & No path/motion-only gestures\\\hline
3.1.1 & Language of Page (A) & \yes & \texttt{lang} attribute set\\\hline
3.1.2 & Language of Parts (AA) & \na & Single-language content\\\hline
3.2.1 & On Focus (A) & \yes & No context change on focus\\\hline
3.2.2 & On Input (A) & \yes & No unexpected change on input\\\hline
3.2.3 & Consistent Navigation (AA) & \yes & Consistent nav across views\\\hline
3.2.4 & Consistent Identification (AA) & \yes & Consistent component labels\\\hline
3.3.1 & Error Identification (A) & \yes & Errors announced + identified\\\hline
3.3.2 & Labels or Instructions (A) & \yes & Labels/instructions on inputs\\\hline
3.3.3 & Error Suggestion (AA) & \conf & Correction guidance on errors\\\hline
3.3.4 & Error Prevention (Legal/Fin/Data) (AA) & \yes & Two-stage confirmation + time-lock + cancel\\\hline
4.1.1 & Parsing (A) & \yes & Valid markup\\\hline
4.1.2 & Name, Role, Value (A) & \yes & ARIA name/role/value on components\\\hline
4.1.3 & Status Messages (AA) & \yes & ARIA live regions announce updates\\\hline
\end{longtable}
\end{center}
{\footnotesize \textit{Note.} 2.2.1 (Timing Adjustable) is the one open conformance item: the 60\,s window is
currently fixed and is flagged in the main paper as requiring user-configurability; two evaluators (E7, E9)
independently raised it. It is the top remediation item for the next iteration.}

\section*{S6. Static Analysis (Slither)}
\texttt{slither} was run against \texttt{HealthAccessControl.sol} (solc~0.8.19); the full JSON report is deposited at \texttt{analysis/slither\_report.json}. All High and Medium findings were reviewed and determined to be false positives for this contract's usage; no change to contract behaviour was required.
\begin{center}\small
\begin{tabular}{|l|c|l|p{6.0cm}|}
\hline\textbf{Severity} & \textbf{Count} & \textbf{Detector(s)} & \textbf{Resolution}\\\hline
High & 1 & \texttt{weak-prng} & False positive: \texttt{block.timestamp} is used only for the 60\,s consent time-lock and for audit-log timestamps, never as a source of randomness; no value or branch depends on unpredictable entropy.\\\hline
Medium & 1 & \texttt{incorrect-equality} & Reviewed: strict equality is applied only to explicit sentinel checks (e.g.\ \texttt{grant.expiration == 0}, denoting ``no expiry''), never to balances or block timestamps; no exploitable path.\\\hline
Low & 10 & \texttt{timestamp}, \texttt{shadowing-local}, \texttt{events-access} & \texttt{block.timestamp} dependence is intrinsic to the documented time-lock design (L7); local shadowing and missing ownership events are non-security style items.\\\hline
Informational & 38 & \texttt{solc-version}, \texttt{naming-convention}, \texttt{boolean-equal} & Style/versioning only; no functional or security impact.\\\hline
\end{tabular}
\end{center}
{\footnotesize Static analysis is a floor, not a substitute for professional audit; the contract remains unaudited by an independent third party (Limitation~L8). Record the exact Slither and solc versions and run date alongside the deposited report.}

\section*{S7. Literature Survey: Search Strategy and Screening Criteria}
Full search strategy underlying the Phase~1 targeted survey (main paper, Section~\ref{sec:methodology}). This is a narrative, motivation-scoping survey, not a systematic literature review; no pre-registered protocol or PRISMA reporting was applied.

\textbf{Databases searched:} IEEE Xplore, ACM Digital Library, SpringerLink, PubMed.

\textbf{Search term clusters} (combined per database query):
\begin{itemize}
\item \textit{Blockchain cluster:} ``blockchain'', ``distributed ledger'', ``smart contract'', ``decentralized''
\item \textit{HCI/UI cluster:} ``human-computer interaction'', ``user interface'', ``usability'', ``accessibility'', ``UI/UX'', ``user experience''
\item \textit{Healthcare/PwD cluster:} ``healthcare'', ``medical records'', ``people with disabilities'', ``assistive technology'', ``inclusive design''
\end{itemize}

\textbf{Screening criteria:} papers were retained if they (a) addressed blockchain in a healthcare or medical context, and (b) discussed interface design, usability, or accessibility in any form. Papers addressing only blockchain infrastructure without any UI/UX component, or focused exclusively on cryptocurrency interfaces without healthcare relevance, were excluded. Screening was conducted by a single reviewer without a second independent rater; the retained sample (34 papers, 2018--2025, plus seminal pre-2018 reference systems) should be read as illustrative of the field rather than a bias-controlled census.
\end{document}
